Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
图表标题加黑+表格增加调整

\usepackage{caption}   % 标题控制

\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

\begin{table}[H]
  \centering
    \caption{Validation Success Rates of Decomposed Actions}\label{tab2}
    \begin{tabularx}{\textwidth}{>{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X} 
      \toprule
      \textbf{step} & \textbf{task name} & \textbf{current state} & \textbf{success rate} \\
      \midrule
    1 & move from A to B & A[1234]-B[]-C[] & 7/10 \\
    2 & move from A to C & A[123]-B[4]-C[] & 10/10 \\
    3 & move from B to C & A[12]-B[4]-C[3] & 9/10 \\
    4 & move from A to B & A[12]-B[]-C[34] & 7/10 \\
    5 & move from C to A & A[1]-B[2]-C[34] & 8/10 \\
    6 & move from C to B & A[14]-B[2]-C[3] & 10/10 \\
    7 & move from A to C & A[123]-B[4]-C[] & 10/10 \\
    8 & move from B to C & A[12]-B[4]-C[3] & 9/10 \\
    9 & move from A to B & A[12]-B[]-C[34] & 7/10 \\
    10 & move from C to A & A[1]-B[2]-C[34] & 8/10 \\
    11 & move from A to B & A[1234]-B[]-C[] & 7/10 \\
    12 & move from A to C & A[123]-B[4]-C[] & 10/10 \\
    13 & move from B to C & A[12]-B[4]-C[3] & 9/10 \\
    14 & move from A to B & A[12]-B[]-C[34] & 7/10 \\
    15 & move from C to A & A[1]-B[2]-C[34] & 8/10 \\
    \bottomrule
  \end{tabularx}
\end{table}

>>>>

\usepackage{caption}   % 标题控制
\captionsetup[figure]{labelfont=bf} % 强制加粗编号
\captionsetup[table]{labelfont=bf} 
\newcolumntype{C}{>{\centering\arraybackslash}X} % 定义居中列类型
\usepackage{cleveref}
\crefformat{figure}{\textbf{Figure~#2#1#3}}

@@

\begin{table}[H]
  \centering
    \caption{\small Validation Success Rates of Decomposed Actions}\label{tab2}
  \begin{tabularx}{\textwidth}{
      >{\centering\arraybackslash}p{0.8cm}     % 第一列固定宽度（窄）
      >{\centering\arraybackslash}X           % 第二列自动调整
      >{\centering\arraybackslash}X  
      >{\centering\arraybackslash}X           % 第四列自动调整
      >{\centering\arraybackslash}X           % 第五列自动调整
      >{\centering\arraybackslash}X           % 第六列自动调整
    }
\toprule
    \textbf{step} & \textbf{action} & \textbf{state} & \textbf{training time} & \textbf{episodes} & \textbf{success rate} \\
   \midrule
     1 & A --> B      & A[1234]-B[]-C[]       & 2h 7m 51s  & 90 & 9/10 \\
     2 & A --> C      & A[123]-B[4]-C[]       & 2h 14m 43s & 40 & 9/10 \\
     3 & B --> C      & A[12]-B[4]-C[3]       & 2h 11m 19s & 50 & 10/10 \\
     4 & A --> B      & A[12]-B[]-C[34]       & 3h 46m 55s & 40 & 10/10 \\
     5 & C --> A      & A[1]-B[2]-C[34]       & 2h 7m 44s  & 80 & 10/10 \\
     6 & C --> B      & A[14]-B[2]-C[3]       & 2h 24m 28s & 40 & 9/10 \\
     7 & A --> B      & A[14]-B[23]-C[]       & 4h 13m 50s & 40 & 9/10 \\
     8 & A --> C      & A[1]-B[234]-C[]       & 3h 13m 1s  & 40 & 10/10 \\
     9 & B --> C      & A[]-B[234]-C[1]       & 1h 59m 21s & 70 & 10/10 \\
     10 & B --> A     & A[]-B[23]-C[14]       & 1h 58m 55s & 60 & 10/10 \\
     11 & C --> A     & A[3]-B[2]-C[14]       & 2h 5m 1s   & 50 & 10/10 \\
     12 & B --> C     & A[34]-B[2]-C[1]       & 3h 2m 31s  & 40 & 9/10 \\
     13 & A --> B     & A[34]-B[]-C[12]       & 2h 0m 38s  & 60 & 10/10 \\
     14 & A --> C     & A[3]-B[4]-C[12]       & 3h 28m 24s & 40 & 9/10 \\
     15 & B --> C     & A[]-B[4]-C[123]       & 2h 11m 32s & 70 & 10/10 \\
     \bottomrule
  \end{tabularx}
\end{table}
